Vod Report

### 2018-11-10 vodnotebook.Rmd
remove tidy eval

@@

### DST

>>>>

```{r}
full_models <- read_rds(here::here("cache", "vod_full_models.Rds"))
full_results <- read_rds(here::here("cache", "vod_full_results.Rds"))
```

```{r}
full_models$model_time_const %>% broom::tidy()
```

@@

### DST 
```{r}
dst_models <- read_rds(here::here("cache", "vod_dst_models.Rds"))
dst_results <- read_rds(here::here("cache", "vod_dst_results.Rds"))

dst_models$model_district_adjusted %>% broom::tidy()
```
